---
title: "linear model from Web"
author: "America Olivo"
date: "Fall 2022"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS

### scatterplot

```{r}
basicNN <- ggplot(data,aes(x=SIMS,y=ARM))
basicNN +geom_point()+ geom_lm()
```


The scatter plot demonstrates a positive linear relationship because the fit line is going to the right and increasing.

### Numerical results


```{r}
cor(SIMS ~ARM, data=data)
```

the correlation is SIMS is positive (0.686) which tells use that we have positive number therefore it has to be positive.

### Inferential  (Build model.1)


```{r}
model.1 <- lm(SIMS~ARM, data=data)
summary.lm(model.1)
```

#### Predict at target point
```{r}
mydat <- data.frame(GRIP = 94, ARM = 88)

```







```{r}
predict(model.1, mydat, interval ="prediction")

```

The target prediction is .70 , the lower interval is -1.70 , and lastly the upper prediction is 3.13


#### scatterplot with model fit

```{r}
basicNN <- ggplot(data,aes(x=SIMS,y=ARM))
basicNN +geom_point()+ geom_lm()
```

## Model 2 SIM~GRIP

### Now add in scatterplot

```{r}
basicNN <- ggplot(data,aes(x=SIMS,y=GRIP))
basicNN +geom_point()+ geom_lm()
```


The scatter plot shows us a positive linear fit for GRIP and SIMS. 


### Numerical results 
```{r}
cor(SIMS ~GRIP, data=data)
```
This number is our linear correlation which is 0.63which means we still have a positive linear correlation. 
### Inferential  (Build model.2)
  
```{r}
model.2<- lm(SIMS~GRIP, data=data)
summary.lm(model.2)
```

#### predict model.2 at target point
```{r}
mydat<- data.frame(GRIP = 94, ARM = 88)
```
```{r}
predict(model.2, mydat, interval ="prediction")

```

The prediction of fit is -0.536 and we got lower as -3.107 and the upper is 2.035. 


#### now add the model fit to our plot for model.2
```{r}
basicNG <- ggplot (data, aes(y=GRIP, x= SIMS))
basicNG + geom_point()+ geom_lm()
```
  


## Model 3 SIM~ARM+GRIP



### Numerical results (cor)

```{r}
cor(SIMS~ARM+GRIP, data=data)
```
The correlation is 0.732 which is a positive number meaning we have a positive linear correlation. 

  
### Inferential  (Build 2-dimentional model.3)

```{r}
model.3 <- lm(SIMS~ARM+GRIP, data=data)
summary.lm(model.3)
```




#### predict model.3 at target point
  

```{r}
predict(model.3,mydat,interval = "prediction")
```
The linear fir is 0.149, lower is -2.132, and the upper is 2.431.

## Comparing nested models ANOVA Test

### Model.1 vs Model.3

```{r}
anova (model.1, model.3)
```

The anova test shows that model 3 is a better fit than model 1.

### Model.2 vs Model.3

```{r}
anova(model.2, model.3)
```

The anova test sgows that model 3 is a better fit than model 2.

## Informally compare Model.1 with model.2
```{r}
anova(model.1, model.2)
```

Model 1 is a better fit than model 2 because of its adjusted r square was lower but neither model shows a p value because they never nested data. The overall best fit model was model 3 because has the highest adjusted r square and the lowest residual error number. We only got one p value form model 3 but its because it had nested data form models 1 and 2. 


